`r glue::glue('inferCNV results for {params$library_id} with {params$reference_name} reference')`

### 2025-05-07 analyses/infercnv-consensus-cell-type/template-notebooks/SCPCP000015_explore-infercnv-results.Rmd
update ridge plot to remove low numbers of cells and include sorted n= labels

* `tumor-endo`: Cells labeled as tumor by cell-type-ewings, but endothelial by `cell-type-consensus`
* `tumor-immune`: Cells labeled as tumor by cell-type-ewings, but immune by `cell-type-consensus`
* `tumor`: Cells labeled as tumor by `cell-type-ewings`
* `endo`: An endothelial cell type
* `immune`: An immune cell type
* If none of the above, their existing `cell-type-ewings` annotation

@@

```{r fig.height=12, message=FALSE, warning=FALSE}
# drop cells from other libraries
query_has_cnv_df <- has_cnv_df |>
  dplyr::filter(library_id == params$library_id)

ggplot(query_has_cnv_df) +
  aes(
    y = celltype,
    x = total_cnv_per_cell,
    fill = cell_group
  ) +
  ggridges::geom_density_ridges2(alpha = 0.7, scale = 0.85)
```

>>>>

* `tumor-endo`: Cells labeled as tumor by cell-type-ewings, but endothelial by `cell-type-consensus`
* `tumor-immune`: Cells labeled as tumor by cell-type-ewings, but immune by `cell-type-consensus`
* `tumor`: Cells labeled as tumor by `cell-type-ewings`
* If none of the above, their existing `cell-type-ewings` annotation

@@

```{r fig.height=8, message=FALSE, warning=FALSE}
# drop cells from other libraries, and update data frame for plotting
query_has_cnv_df <- has_cnv_df |>
  dplyr::filter(library_id == params$library_id) |>
  dplyr::add_count(celltype) |>
  # remove really low count cell types
  dplyr::filter(n >= 3) |>
  # add column with cell type counts, and arrange in order
  dplyr::mutate(
    celltype_n = glue::glue("{celltype} (n={n})"),
    celltype_n = forcats::fct_infreq(celltype_n),
    celltype_n = forcats::fct_rev(celltype_n)
  )

ggplot(query_has_cnv_df) +
  aes(x = total_cnv_per_cell, y = celltype_n) +
  ggridges::geom_density_ridges2(alpha = 0.7, scale = 0.85)
```
